Disparity peaks

### 2017-12-11 analyses/09-figure-peaks.Rmd
Switch X and Y labels

---
title: "Disparity peaks and troughs"
author: "Natalie Cooper"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_width: 12
    fig_height: 12
---

@@

pdf("../manuscript/figures/fig-peaks-epoch.pdf")  
  multiplot(beck_peaks + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            brusatte_peaks + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            bapst_peaks + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            wright_peaks + theme(plot.margin=unit(c(5.5, 5.5, 20, 25),"points")),
            cols = 1,
            labs = list("Time at disparity peak (MYA)", 
                        "Time bins or time slice method"),
            labpos = list(c(0.5, 0.015), c(0.03, 0.5)))

@@

pdf("../manuscript/figures/fig-peaks-age.pdf")  
  multiplot(beck_peaks_age + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            brusatte_peaks_age + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            bapst_peaks_age + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            wright_peaks_age + theme(plot.margin=unit(c(5.5, 5.5, 20, 25),"points")),
            cols = 1,
            labs = list("Time at disparity peak (MYA)", 
                        "Time bins or time slice method"),
            labpos = list(c(0.5, 0.015), c(0.03, 0.5)))

@@

pdf("../manuscript/figures/fig-peaks-epoch-appendix.pdf")  
  multiplot(beck_peaks + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            brusatte_peaks + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            bapst_peaks + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            wright_peaks + theme(plot.margin=unit(c(5.5, 5.5, 20, 25),"points")),
            cols = 1,
            labs = list("Time at disparity peak (MYA)", 
                        "Time bins or time slice method"),
            labpos = list(c(0.5, 0.015), c(0.03, 0.5)))

@@

pdf("../manuscript/figures/fig-peaks-age-appendix.pdf")  
  multiplot(beck_peaks_age + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            brusatte_peaks_age + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            bapst_peaks_age + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            wright_peaks_age + theme(plot.margin=unit(c(5.5, 5.5, 20, 25),"points")),
            cols = 1,
            labs = list("Time at disparity peak (MYA)", 
                        "Time bins or time slice method"),
            labpos = list(c(0.5, 0.015), c(0.03, 0.5)))

>>>>

---
title: "Disparity peaks"
author: "Natalie Cooper"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_width: 12
    fig_height: 12
---

@@

pdf("../manuscript/figures/fig-peaks-epoch.pdf")  
  multiplot(beck_peaks + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            brusatte_peaks + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            bapst_peaks + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            wright_peaks + theme(plot.margin=unit(c(5.5, 5.5, 20, 25),"points")),
            cols = 1,
            labs = list("Time bins or time slice method",
                        "Time at disparity peak (MYA)"),
            labpos = list(c(0.5, 0.015), c(0.03, 0.5)))

@@

pdf("../manuscript/figures/fig-peaks-age.pdf")  
  multiplot(beck_peaks_age + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            brusatte_peaks_age + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            bapst_peaks_age + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            wright_peaks_age + theme(plot.margin=unit(c(5.5, 5.5, 20, 25),"points")),
            cols = 1,
            labs = list("Time bins or time slice method",
                        "Time at disparity peak (MYA)"),
            labpos = list(c(0.5, 0.015), c(0.03, 0.5)))

@@

pdf("../manuscript/figures/fig-peaks-epoch-appendix.pdf")  
  multiplot(beck_peaks + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            brusatte_peaks + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            bapst_peaks + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            wright_peaks + theme(plot.margin=unit(c(5.5, 5.5, 20, 25),"points")),
            cols = 1,
            labs = list("Time bins or time slice method",
                        "Time at disparity peak (MYA)"),
            labpos = list(c(0.5, 0.015), c(0.03, 0.5)))

@@

pdf("../manuscript/figures/fig-peaks-age-appendix.pdf")  
  multiplot(beck_peaks_age + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            brusatte_peaks_age + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            bapst_peaks_age + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            wright_peaks_age + theme(plot.margin=unit(c(5.5, 5.5, 20, 25),"points")),
            cols = 1,
            labs = list("Time bins or time slice method",
                        "Time at disparity peak (MYA)"),
            labpos = list(c(0.5, 0.015), c(0.03, 0.5)))
